%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Ayush Kumar}{Shaw}{ \urlstyle{same}\href{https://www.linkedin.com/in/ayush-shaw/}{linkedin.com/in/ayush-shaw/}\\
\href{mailto:ayushshawz@gmail.com}{ayushshawz@gmail.com} | \href{tel:919831284491}{+91 98312-84491}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
Java \textbullet{} HTML \textbullet{} CSS \textbullet{} Javascript \\
\textbullet{} C \textbullet{} C++ \textbullet{} Python 
\textbullet{} Shell \textbullet{} SQL \\

\subsection{Frameworks}
Spring \textbullet{} Spring Boot\\

\subsection{Tools}
Git \textbullet{} GitHub  \textbullet{} GitLab  \textbullet{} Mockito \\ \textbullet{} JUnit \textbullet{} Apache Tomcat  \textbullet{} LaTeX \\ \textbullet{} jQuery \textbullet{} JDBC \textbullet{} Gradle \textbullet{} Wireshark \\ \textbullet{} Postman\textbullet{} IntelliJ IDEA \textbullet{} VSCode \\ \textbullet{} Eclipse \textbullet{} Sublime Text
\sectionsep

\subsection{DBMS}
Oracle \textbullet{} MySQL \textbullet{} MongoDB
\sectionsep

\subsection{Platforms}
Linux \textbullet{} GCP 
\sectionsep

\subsection{Soft Skills}
Leadership \textbullet{} Writing 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
LinkedIn://  \href{https://www.linkedin.com/in/ayush-shaw}{\bf ayush-shaw} \\
GitHub://  \href{https://github.com/Ak-Shaw}{\bf Ak-Shaw} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{BGI - SDET}
\descript{B. Tech in Computer Science \\ and Engineering}
\location{June 2021 | West Bengal, India}
\location{ Cum. GPA: 8.98 / 10.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\subsection{Undergraduate}
\sectionsep
Database Management System \\
Computer Networks \\
Operating Systems \\
Object Oriented Programming \\
Data Structures \& Algorithms \\
Design \& Analysis of Algorithms \\
Digital Electronics \\
Discrete Mathematics \\
Computer Organisation \\
Computer Architecture \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Crio.Do}
\descript{| Software Engineer (Content) - Intern }
\location{Nov 2020 | Remote}

\runsubsection{Crio.Do}
\descript{| Student Developer (Crio Launch Plus 2020) - Trainee }
\location{Apr 2020 - Aug 2020 | Remote}
Contributed to a scalable distributed back-end of a food ordering application and constructed APIs for a quiz application.\\

\runsubsection{Crio.Do}
\descript{| Student Developer (Crio Launch 2020) - Trainee }
\location{Feb 2020 - Apr 2020 | Remote}
Contributed to these projects: a secure file-sharing service, a visual stock portfolio analyzer, and an online IDE.\\

\textbf{Portfolio showcasing contributions as a student developer:} \href{https://criodo.github.io/portfolio-ayushshawz/}{criodo.github.io/portfolio-ayushshawz/}\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Visual stock portfolio analyzer}\\
\location{Mar 2020 – Apr 2020 | Guided Individual Project}
\sectionsep
\begin{tightemize}
% \item Has prospects to aid portfolio managers for making better trade recommendations for their clients.
\item Stock quote services were addressed via \textbf{REST APIs}.
\item \textbf{Refactored} code \textbf{to adapt} to an \textbf{updated interface contract} published by the back-end team.
\item Brought \textbf{comprehensive error reporting} and better \textbf{exception handling} into picture, which further \textbf{improved application stability}.
\item \textbf{Multi-threading} was introduced to improve application responsiveness.
\item \textbf{JAR} publication of the portfolio manager library was concluded.
\end{tightemize}
\sectionsep

\runsubsection{Secure file-sharing service}\\
\location{Feb 2020 – Apr 2020 | Guided Individual Project}
\begin{tightemize}
\item Implemented a \textbf{pre-installation script} that \textbf{validated the minimum system requirements} to be met for the customised \textbf{VSFTPD} server installation. The script checked the \textbf{availability} of required \textbf{processor}, \textbf{memory}, \textbf{disk space}, and \textbf{OS version}.
\item \textbf{Identified regressions} in newer versions of the server.
\item Performance issues were debugged by \textbf{monitoring} the \textbf{memory usage}, \textbf{cpu usage}, \textbf{file transfer speed}, and \textbf{file permission issues}.
\item Analyzed collected \textbf{pcap} files using \textbf{Wireshark} to troubleshoot the following network issues: \textbf{TCP retransmissions}, \textbf{connection refusals}, \textbf{dropped connections}, \textbf{sub-optimal TCP window sizes} and \textbf{retransmission delays}.
\item Created \textbf{SSL} certificates to enable end-to-end encryption.
\item In order to \textbf{ensure encryption}, snooped the network traffic using \textbf{Wireshark}.
\end{tightemize}
\sectionsep

\runsubsection{Food ordering application}\\
\location{Jan 2020 – Aug 2020 | Guided Individual Project}
\begin{tightemize}
\item Adapted \textbf{Spring Boot} for building a distributed \textbf{Java} back-end.
\item Adhered to \textbf{MVCS} layering. 
\item \textbf{MongoDB} aided storage, from which a list of nearby restaurants was retrieved, based on user location.
\item Implemented a simple \textbf{REST API} and the corresponding request handler and response methods.
\item Code reliability was demonstrated, utilizing \textbf{JUnit} and \textbf{Mockito} behind the scenes.
\item Executed Facebook Share API, Pinterest Share API, and Clarifai API.
\end{tightemize}
\sectionsep

% \runsubsection{Quiz application}\\
% \location{Aug 2020 | Guided Individual Project}
% \begin{tightemize}
% \item Assembled \textbf{GET} and \textbf{POST} API with \textbf{Spring Boot} construct.
% \item \textbf{MongoDB} aided the backend.
% \item Usage of \textbf{Postman} verified the implementation of the APIs.
% \item Code reliability was demonstrated, utilizing \textbf{JUnit} and \textbf{Mockito} behind the scenes.
% \end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Accomplishments
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Accomplishments} 
% \sectionsep
% \subsection{TCS Codevita Season 8 Round 1 | India zone 1}
% \subsection{RANK: 574 OUT OF 2562}
% \location{Aug 2019}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certifications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Certifications} 
% \sectionsep
% \subsection{Problem Solving Through Programming in C}
% NPTEL18CS10S3510040 \\
% \location{May 2018}
% \sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}
