%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Ayush Kumar}{Shaw}{ \urlstyle{same}\href{https://www.linkedin.com/in/ayush-shaw/}{linkedin.com/in/ayush-shaw/}\\
\href{mailto:ayushshawz@gmail.com}{ayushshawz@gmail.com} | \href{tel:919831284491}{+91 98312-84491}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
Java \textbullet{} HTML \textbullet{} CSS \textbullet{} Javascript \\
\textbullet{} C \textbullet{} C++ \textbullet{} Python 
\textbullet{} Shell \textbullet{} SQL \\

\subsection{Frameworks}
Spring \textbullet{} Spring Boot\\

\subsection{Tools}
Git \textbullet{} GitHub  \textbullet{} GitLab  \textbullet{} Mockito \\ \textbullet{} JUnit \textbullet{} Apache Tomcat  \textbullet{} LaTeX \\ \textbullet{} jQuery \textbullet{} JDBC \textbullet{} Gradle \textbullet{} Wireshark \\ \textbullet{} Postman\textbullet{} IntelliJ IDEA \textbullet{} VSCode \\ \textbullet{} Eclipse \textbullet{} Sublime Text
\sectionsep

\subsection{DBMS}
Oracle \textbullet{} MySQL \textbullet{} MongoDB
\sectionsep

\subsection{Platforms}
Linux \textbullet{} GCP 
\sectionsep

\subsection{Soft Skills}
Leadership \textbullet{} Writing \\ 
\textbullet{} Time Management
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
LinkedIn://  \href{https://www.linkedin.com/in/ayush-shaw}{\bf ayush-shaw} \\
GitHub://  \href{https://github.com/Ak-Shaw}{\bf Ak-Shaw} \\
Twitter://  \href{https://twitter.com/Ayush_Shaw_z}{\bf @Ayush\_Shaw\_z} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{BGI - SDET}
\descript{B. Tech in Computer Science \\ and Engineering}
\location{June 2021 | West Bengal, India}
\location{ Cum. GPA: 7.8 / 10.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\subsection{Undergraduate}
\sectionsep
Database Management System \\
Computer Networks \\
Operating Systems \\
Object Oriented Programming \\
Data Structures \& Algorithms \\
Design \& Analysis of Algorithms \\
Digital Electronics \\
Discrete Mathematics \\
Computer Organisation \\
Computer Architecture \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Crio.Do}
\descript{| Student Developer ( Crio Launch 2020 ) }
\location{Jan 2020 - Apr 2020 | Remote}
Contributed to these projects: a secure file-sharing service, a visual stock portfolio analyzer, and an online IDE.\\
\textbf{Portfolio showcasing contributions:} \href{https://criodo.github.io/Crio-Launch-Feb-2020-ayushshawz/}{criodo.github.io/Crio-Launch-Feb-2020-ayushshawz/}\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Visual stock portfolio analyzer}\\
\location{Mar 2020 – Apr 2020 | Guided Individual Project}
\sectionsep
\begin{tightemize}
\item Developed to help portfolio managers make trade recommendations for their clients.
\item Utilized stock quote services via \textbf{REST APIs}.
\item Published the portfolio manager library as a \textbf{JAR}.
\end{tightemize}
\sectionsep

\runsubsection{Food ordering application}\\
\location{Jan 2020 – Aug 2020 | Guided Individual Project}
\begin{tightemize}
\item Built a distributed \textbf{Java} back-end.
\item Adhered to \textbf{MVCS} layering. 
\item \textbf{MongoDB} aided storage. 
\item Utilized \textbf{JUnit} and \textbf{Mockito} for testing.
\item Executed Facebook Share API, Pinterest Share API, and Clarifai API.
\end{tightemize}
\sectionsep

\runsubsection{Secure file-sharing service}\\
\location{Feb 2020 – Apr 2020 | Guided Individual Project}
\begin{tightemize}
\item Installed a customized version of the \textbf{VSFTPD} server.
\item Debugged performance issues.
\item Troubleshot network issues by collecting and analyzing \textbf{pcap} files using \textbf{Wireshark}. 
\item Enabled end-to-end encryption by creating \textbf{SSL} certificates.
\end{tightemize}
\sectionsep

\runsubsection{Quiz application}\\
\location{Aug 2020 | Guided Individual Project}
\begin{tightemize}
\item Created \textbf{API} for \textbf{GET} and \textbf{POST} request.
\item Utilized \textbf{Spring Boot} along with \textbf{MongoDB}.
\item Usage of \textbf{Postman} verified the implementation of the APIs.
\item Wrote unit test cases to demonstrate code reliability by utilizing \textbf{JUnit} and \textbf{Mockito}.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Accomplishments
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Accomplishments} 
\sectionsep
\subsection{TCS Codevita Season 8 Round 1 | India zone 1}
\subsection{RANK: 574 OUT OF 2562}
\location{Aug 2019}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Certifications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Certifications} 
\sectionsep
\subsection{Problem Solving Through Programming in C}
NPTEL18CS10S3510040 \\
\location{May 2018}
\sectionsep


\end{minipage} 
\end{document}  \documentclass[]{article}
